Generalists are the most urban-tolerant of birds: a phylogenetically controlled analysis of ecological and life-history traits using a novel continuous urbanization index

### 2018-06-12 ms.Rmd
More minor edits

## Differences in non-phylogenetic and phylogenetic models
Non-phylogenetic and phylogenetic models largely agreed in the relative rank of standardized predictor estimates (Appendix 5) and the statistical significance of individual predictors (Fig. 4; Appendix 5). However, residual brain size was not significant in either non-phylogenetic models (Fig. 4), but was significantly associated with urbanization in our phylogenetic models, showing the strongest relative response in the phylogenetic global model (Fig. 4; Fig. 5). Further, diet generalism, feeding habitat generalism, and breeding habitat generalism were relatively more important (large standardized parameter estimates) in the phylogenetic models, compared with the non-phylogenetic models (Fig. 5; Appendix 5). Lastly, although not significant, body size was minimally important for the non-phylogenetic model, but substantially more important for the phylogenetically controlled models (Fig. 4 & Fig. 5).

>>>>

## Differences in non-phylogenetic and phylogenetic models
Non-phylogenetic and phylogenetic models largely agreed in the relative rank of standardized predictor estimates (Appendix 5) and the statistical significance of individual predictors (Fig. 4; Appendix 5). However, residual brain size was not significant in either non-phylogenetic model approaches (Fig. 4), but was significantly associated with urbanization in our phylogenetic modelling, showing the strongest relative response in the phylogenetic global model (Fig. 4; Fig. 5). Further, diet generalism, feeding habitat generalism, and breeding habitat generalism were relatively more important (large standardized parameter estimates) in the phylogenetic models, compared with the non-phylogenetic models (Fig. 5; Appendix 5). Lastly, although not significant, body size was minimally important for the non-phylogenetic models, but substantially more important for the phylogenetically controlled models (Fig. 4 & Fig. 5).
